### 2025-07-01 paper/sections/other/main_results.qmd
ok now
getting a little stuck here

@@

Final hyperparameters used for the main results preseneted in @sec-experiments. Any hyperparameter not shown here is set to its default value (@nte-train-default).

@@

![The same setup, factuals, model architecture and generator as in @fig-mnist, but the model was trained with CT.](/paper/figures/mnist_mlp_vanilla.png){#fig-mnist-vanilla}
:::

>>>>

\FloatBarrier

@@

Final hyperparameters used for the main results presented in @sec-experiments. Any hyperparameter not shown here is set to its default value (@nte-train-default).

@@

![The same setup, factuals, model architecture and generator as in @fig-mnist, but the model was trained conventionally.](/paper/figures/mnist_mlp_vanilla.png){#fig-mnist-vanilla}
:::
